---
title: "Tidyverse"
author: "Kayenat Farheen"
---

::: callout-note

:::

This is the code for the first tidyverse challenge



# Text Formatting

*italics* and **bold**

superscript^2^ / subscript~2~

~~strikethrough~~

`verbatim code`

> Blockquote

# Headings



# Links & Images

# Source Code

Use ``` to delimit blocks of source code:

```
code
```
```{r}

library(tidyverse)
library(readxl)
library(dplyr)
library(ggplot2)
library(writexl)
```

```{r}
# 2.0 Importing Files ----
bike=read_excel("bikes.xlsx")
bikeshops=read_excel("bikeshops.xlsx")
orderlines=read_excel("orderlines.xlsx")

```



```{r}
joined_grp3=left_join(orderlines,bikeshops,by=c("customer.id"="bikeshop.id"))
joined_grp4=left_join(joined_grp3,bike,by=c("product.id"="bike.id"))
joined_grp4=mutate(joined_grp4,total_price=price*quantity)
glimpse(joined_grp4)
joined_grp4=separate(joined_grp4,col="location",into=c("city","state"),",")
glimpse(joined_grp4)
joined_grp4=mutate(joined_grp4,year=year(order.date))
joined_grp5=joined_grp4 %>% select(state,total_price,city,year)
joined_grp5=group_by(joined_grp5,state)
joined_grp5=summarise(joined_grp5,sales=sum(total_price))
max_state=joined_grp5$state[which.max(joined_grp5$sales)]
max_state

```
Plotting
```{r}

ggplot(joined_grp5,aes(state,sales))+geom_col(fill="pink") + theme(axis.text.x = element_text(angle = 45, hjust = 1))
bike_orderlines_wrangled_tbl=joined_grp5
joined_grp6=group_by(joined_grp4,year,state)
joined_grp6=summarise(joined_grp6,sales=sum(total_price))
ggplot(joined_grp6,aes(year,sales,fill=state))+geom_col()+facet_wrap(~ state) +theme(axis.text.x = element_text(angle = 45, hjust = 1))
state_sales_wrangled=joined_grp6
```

```{r}

```
